Information and Airbnb, An Analysis on the Impact of Reviews and Ratings on Airbnb Prices in Canada

### 2024-02-15 outputs/paper.qmd

@@

```{r}
#| echo: false
airbnb <- read_csv("~/airbnbtp2/inputs/data/airbnb_cleaned_data.csv")
```

>>>>

In the changing landscape of modern travel, Airbnb has emerged as a transformative force, reshaping traditional notions of accommodation and hospitality. Central to Airbnb's allure are the wealth of user-generated reviews and ratings, which serve as vital sources of information for prospective guests navigating a vast array of listings. These reviews not only offer insights into the quality and character of accommodations but also play a pivotal role in shaping consumer decisions. However, amidst this burgeoning ecosystem of shared experiences, a fundamental question persists: What precise impact do these reviews and ratings wield on Airbnb pricing strategies? This question lies at the heart of our inquiry, as we delve into the intricate interplay between information dissemination, consumer behavior, and pricing dynamics within the Airbnb marketplace. Through rigorous statistical analysis, this paper endeavors to unravel the nuanced relationship between reviews, ratings, and Airbnb prices, shedding light on an increasingly critical facet of the sharing economy.

@@

```{r}
#| echo: false
#|
airbnb <- read_csv("/airbnb/inputs/data/airbnb_cleaned_data.csv")
```
